---
title: "2. Analysis of Price, Appraisal offers, Market, and Online appraisal flag"
author: "Sumit Kumar Kar"
date: "1/13/2023"
output: html_document
tables: true
header-includes:
- \usepackage{caption}
- \captionsetup[table]{labelformat=empty}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Reading the data
library(readr)
derived_data <- readRDS("My_Data/derived_df.rds")
```

```{r, include=FALSE}
# Loading necessary libraries
library(mosaic) # necessary for functions like tally, etc.
```

# Relation between Appraisal offer and Price

```{r, echo = FALSE}
table_p <- tally(derived_data$price)
table_p[order(table_p, decreasing = TRUE)]/200000*100
```

```{r, echo = FALSE}
table_ao <- tally(derived_data$appraisal_offer1)
table_ao[order(table_ao, decreasing = TRUE)]/200000*100
```

Contingency table between Appraisal offer and Price
```{r, echo = FALSE}
table_ao_p <- table(derived_data$appraisal_offer1, derived_data$price)
table_ao_p
```

Heat map between Appraisal offer and Price

```{r, echo=FALSE}
heatmap(t(table_ao_p), # Draw heat map without dendrograms
        Rowv = NA,
        Colv = NA, xlab = "Appraisal offer", ylab = "Price", main = "Heat map between Appraisal offer and Price")
```

We can see that price of purchased cars increases with appraised values.

Chi-squared test between Appraisal offer and Price

```{r}
chisq.test(derived_data$price, derived_data$appraisal_offer1)
```
The p-value is very small, which implies that Appraisal offer and Price are dependent.

# Relation between Market and Price/Appraisal offer

Let us see the percentage of transactions done in each market (in decreasing order).
```{r, echo = FALSE}
table_m <- tally(derived_data$market)
table_m[order(table_m, decreasing = TRUE)]/200000*100
```
The above table shows that the maximum number of transactions takes place in Market 14 and the minimum in Market 13. 

Contingency table between Market and Price
```{r, echo = FALSE}
table_m_p <- table(derived_data$market, derived_data$price)
table_m_p
```

Heat map between Market and Price

```{r, echo=FALSE}
#par(mar = c(5, 4, 2, 2) + 0.1)
heatmap(t(table_m_p), # Draw heat map without dendrograms
        Rowv = NA,
        Colv = NA, xlab = "Market", ylab = "Price", main = "Heat map between Market and Price")
```

Chi-squared test between Market and Price

```{r}
chisq.test(derived_data$price, derived_data$market)
```
The p-value is very small, which implies that Market and Price are dependent.

Contingency table between Market and Appraisal offer

```{r, echo = FALSE}
table_m_ao <- table(derived_data$market, derived_data$appraisal_offer1)
table_m_ao
```

Heat map between Market and Appraisal offer

```{r, echo=FALSE}
heatmap(t(table_m_ao), # Draw heat map without dendrograms
        Rowv = NA,
        Colv = NA, xlab = "Market", ylab = "Price", main = "Heat map between Market and Appraisal offer")
```

Chi-squared test between Market and Appraisal offer

```{r}
chisq.test(derived_data$appraisal_offer1, derived_data$market)
```
The p-value is very small, which implies that Market and Appraisal offer are dependent.

# Relation between Online appraisal flag and Price/Appraisal offer

Let us see the percentages of transactions done online vs. in-person

```{r, echo=FALSE}
tally(derived_data$online_appraisal_flag)/200000*100
```
The above table shows that 73% of the transactions took place in-person and 25% online. Let us make bar plots to check the price and appraisal offer for two types of transactions (we will exclude the null values, i.e., for which online/in-person is not known).

```{r, echo=FALSE}
# Removing the null values
derived_data_oaf = subset(derived_data, derived_data$online_appraisal_flag != 'null')

tally_oaf_p <- tally(online_appraisal_flag ~ price, data=derived_data_oaf)
barplot(tally_oaf_p, beside = TRUE, legend = TRUE, xlab = "Price", ylab = "Number of cars", main = "Barplot between Online appraisal flag and Price")

tally_oaf_ao <- tally(online_appraisal_flag ~ appraisal_offer1, data=derived_data_oaf)
barplot(tally_oaf_ao, beside = TRUE, legend = TRUE, xlab = "Appraisal offer", ylab = "Number of cars", main = "Barplot between Online appraisal flag and Appraisal offer")
```

The above bar plot shows that for cars of each price range and each appraisal offer range, more transactions occur in-person compared to online.

Chi-squared tests between Online appraisal flag and Price/Appraisal offer

```{r}
chisq.test(derived_data$price, derived_data$online_appraisal_flag)
chisq.test(derived_data$appraisal_offer1, derived_data$online_appraisal_flag)
```
The p-values are very small, which implies that both Price and Appraisal offer are dependent on Online appraisal flag.


# Relation between Online appraisal flag and Market

Let us make bar plots to check the two types of transactions in each market (we will exclude the null values, i.e., for which online/in-person is not known).

```{r, echo=FALSE}
tally_oaf_m <- tally(online_appraisal_flag ~ market, data=derived_data_oaf)
barplot(tally_oaf_m, beside = TRUE, legend = TRUE, xlab = "Market", ylab = "Number of cars", main = "Barplot between Online appraisal flag and Market")
```

The above bar plot shows that in each market, more transactions occur in-person compared to online.

Chi-squared test between Online appraisal flag and Market

```{r}
chisq.test(derived_data$market, derived_data$online_appraisal_flag)
```
The p-value is very small, which implies that Appraisal offer and Market are dependent.
