---
title: "3. Variable-wise comparison between Purchased and Aprraised cars"
author: "Sumit Kumar Kar"
date: "1/14/2023"
output: html_document
tables: true
header-includes:
- \usepackage{caption}
- \captionsetup[table]{labelformat=empty}
---

In this file, I will do side by side plot of the variables common to the appraised and purchased cars. I will also do some additional exploration for these variables to make some conclusions that will be summarized in the final report.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Reading the data
library(readr)
derived_data <- readRDS("My_Data/derived_df.rds")

```

```{r, include=FALSE}
# Loading necessary libraries
library(mosaic) # necessary for functions like tally, etc.
```

# Side-by-side plots of each variable

## Model year

```{r, echo=FALSE}
# Model year
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
hist(derived_data$model_year, xlab = "Model year", ylab = "Number of cars", main = "Purchased")
hist(derived_data$model_year_appraisal, xlab = "Model year", ylab = "Number of cars", main = "Appraised")
```


```{r}
hist(derived_data$model_year-derived_data$model_year_appraisal)
summary(derived_data$model_year-derived_data$model_year_appraisal)
sum(derived_data$model_year<derived_data$model_year_appraisal+4)/200000*100
```
The above results show that Model year of a person’s purchased car can be between 21 years older to 27 years younger than the appraised car. But 75% of the people purchase cars
at least 1 year younger than the appraised car and 50% of the people purchase car at least 4 years younger than the appraised car.

## Mileage

```{r, echo=FALSE}
# Mileage
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$mileage1), xlab = "Mileage", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$mileage_appraisal1), xlab = "Mileage", ylab = "Number of cars", main = "Appraised")
```
## Make

```{r, echo=FALSE}
# Make
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$make), xlab = "Make", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$make_appraisal), xlab = "Make", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$make == derived_data$make_appraisal)/200000*100
sum(derived_data$make != derived_data$make_appraisal)/200000*100
```
This shows that 18% people purchase a car with same make as the appraised car.

## Model

```{r, echo=FALSE}
# Model
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$model), xlab = "Model", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$model_appraisal), xlab = "Model", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$model == derived_data$model_appraisal)/200000*100
sum(derived_data$model != derived_data$model_appraisal)/200000*100
```
```{r}
sum(derived_data$model == derived_data$model_appraisal & derived_data$make == derived_data$make_appraisal)/200000*100
```
This shows that 6.27% people stick to the same model too.

## Trim description

```{r, echo=FALSE}
# Trim description
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$trim_descrip), xlab = "Trim description", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$trim_descrip_appraisal), xlab = "Trim description", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$trim_descrip == derived_data$trim_descrip_appraisal & derived_data$trim_descrip_appraisal != "null" & derived_data$trim_descrip != "null")/200000*100
```

```{r}
tally(trim_descrip ~ trim_descrip_appraisal, data = derived_data)/200000*100
```
This shows that not only 44% people stick to the same trim description, but also 20% people trade in a non-premium car to purchase a premium car. But most surprisingly, 12% people actually trade in a premium car to purchase a non-premium car.

## Body

```{r, echo=FALSE}
# Body
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$body), xlab = "Body", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$body_appraisal), xlab = "Body", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$body == derived_data$body_appraisal & derived_data$body_appraisal != "null" & derived_data$body != "null")/200000*100
```
This shows that 45% people purchase a car with same body as the appraised car.

## Color

```{r, echo=FALSE}
# Color
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$color), xlab = "Color", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$color_appraisal), xlab = "Color", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$color == derived_data$color_appraisal & derived_data$color_appraisal != "null" & derived_data$color != "null")/200000*100
a <- sum(derived_data$color == derived_data$color_appraisal & (derived_data$color == "Black" |derived_data$color == "Gray" |derived_data$color == "Silver" |derived_data$color == "White" ))
b <- sum(derived_data$color != derived_data$color_appraisal & (derived_data$color == "Black" |derived_data$color == "Gray" |derived_data$color == "Silver" |derived_data$color == "White" ))
a/(a+b)*100
```

```{r, echo = FALSE}
table_c <- tally(derived_data$color)
table_c[order(table_c, decreasing = TRUE)]/200000*100
```

```{r, echo = FALSE}
table_ca <- tally(derived_data$color_appraisal)
table_ca[order(table_ca, decreasing = TRUE)]/200000*100
```
This shows thta be it a purchased or an appraised car, the most popular colors are white and black, followed by gray, and silver respectively. In fact, 76% people purchase a car out of these colors and 70% appraise a car out of these 4 colors. Also, 19% people purchase the same color.

## Engine

```{r, echo=FALSE}
# Engine
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
barplot(tally(derived_data$engine), xlab = "Engine", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$engine_appraisal), xlab = "Engine", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$engine == derived_data$engine_appraisal & derived_data$engine_appraisal != "null" & derived_data$engine != "null")/200000*100
```
This shows that 15% people purchase the same engine type.

## Cylinders

```{r, echo=FALSE}
# Cylinders
par(mfrow=c(2,2))    # set the plotting area into a 2*2 array
barplot(tally(derived_data$cylinders), xlab = "Cylinders", ylab = "Number of cars", main = "Purchased")
barplot(tally(derived_data$cylinders_appraisal), xlab = "Cylinders", ylab = "Number of cars", main = "Appraised")

hist(derived_data$cylinders, xlab = "Cylinders", ylab = "Number of cars", main = "Purchased")
hist(derived_data$cylinders_appraisal, xlab = "Cylinders", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$cylinders == derived_data$cylinders_appraisal & derived_data$cylinders_appraisal != "null" & derived_data$cylinders != "null")/200000*100
derived_data_c = subset(derived_data, derived_data$cylinders_appraisal != "null" & derived_data$cylinders != "null")
```
```{r, echo = FALSE}
table_cyl <- tally(derived_data$cylinders)
table_cyl[order(table_cyl, decreasing = TRUE)]/200000*100
```
```{r, echo = FALSE}
table_cyla <- tally(derived_data$cylinders_appraisal)
table_cyla[order(table_cyla, decreasing = TRUE)]/200000*100
```
This shows that 53% people purchase the same number of cylinders. Be it a purchased or an appraised car, the most popular number of cylinders is 4, followed by 6 and 8 respectively. In fact, 99% of the (both purchased and appraised) cars have one of these 3 options and more than 55% cars have 4 cylinders.

## City mpg

```{r, echo=FALSE}
# City mpg
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
hist(derived_data$mpg_city[derived_data$mpg_city!="null"], xlab = "City mpg", ylab = "Number of cars", main = "Purchased")
hist(derived_data$mpg_city_appraisal[derived_data$mpg_city_appraisal!="null"], xlab = "City mpg", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$mpg_city < derived_data$mpg_city_appraisal & is.na(derived_data$mpg_city) == FALSE & is.na(derived_data$mpg_city_appraisal) == FALSE)/200000*100
sum(derived_data$mpg_city > derived_data$mpg_city_appraisal & is.na(derived_data$mpg_city) == FALSE & is.na(derived_data$mpg_city_appraisal) == FALSE)/200000*100
t.test(derived_data$mpg_city, derived_data$mpg_city_appraisal, paired = TRUE)
```
This shows that there is a significant difference between the city mpg of appraised and purchased cars.

## Highway mpg

```{r, echo=FALSE}
# Highway mpg
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
hist(derived_data$mpg_highway, xlab = "Highway mpg", ylab = "Number of cars", main = "Purchased")
hist(derived_data$mpg_highway_appraisal, xlab = "Highway mpg", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$mpg_highway < derived_data$mpg_highway_appraisal & is.na(derived_data$mpg_highway) == FALSE & is.na(derived_data$mpg_highway_appraisal) == FALSE)/200000*100
sum(derived_data$mpg_highway > derived_data$mpg_highway_appraisal & is.na(derived_data$mpg_highway) == FALSE & is.na(derived_data$mpg_highway_appraisal) == FALSE)/200000*100
t.test(derived_data$mpg_highway, derived_data$mpg_highway_appraisal, paired = TRUE)
```
This shows that there is a significant difference between the highwatympg of appraised and purchased cars.

## Horsepower

```{r, echo=FALSE}
# Horsepower
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
hist(derived_data$horsepower, xlab = "Horsepower", ylab = "Number of cars", main = "Purchased")
hist(derived_data$horsepower_appraisal, xlab = "Horsepower", ylab = "Number of cars", main = "Appraised")
```

```{r}
sum(derived_data$horsepower < derived_data$horsepower_appraisal & is.na(derived_data$horsepower) == FALSE & is.na(derived_data$horsepower_appraisal) == FALSE)/200000*100
sum(derived_data$horsepower > derived_data$horsepower_appraisal & is.na(derived_data$horsepower) == FALSE & is.na(derived_data$horsepower_appraisal) == FALSE)/200000*100
t.test(derived_data$horsepower, derived_data$horsepower_appraisal, paired = TRUE)
```
This shows that there is a significant difference between the horsepower of appraised and purchased cars.

## Fuel capacity

```{r, echo=FALSE}
# Fuel capacity
par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
hist(derived_data$fuel_capacity, xlab = "Fuel capacity", ylab = "Number of cars", main = "Purchased")
hist(derived_data$fuel_capacity_appraisal, xlab = "Fuel capacity", ylab = "Number of cars", main = "Appraised")
```
```{r}
sum(derived_data$fuel_capacity < derived_data$fuel_capacity_appraisal & is.na(derived_data$fuel_capacity) == FALSE & is.na(derived_data$fuel_capacity_appraisal) == FALSE)/200000*100
sum(derived_data$fuel_capacity > derived_data$fuel_capacity_appraisal & is.na(derived_data$fuel_capacity) == FALSE & is.na(derived_data$fuel_capacity_appraisal) == FALSE)/200000*100
t.test(derived_data$fuel_capacity, derived_data$fuel_capacity_appraisal, paired = TRUE)
```

This shows that there is no (statistically) significant difference in the fuel capacity of the purchased car and appraised car of a person.